%%https://www.overleaf.com/6237582vwdsfv
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 	TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Prasanna Kumar}{Srinivasachar}{ \urlstyle{same}\url{} \\
\href{mailto:prasanna.310892@gmail.com}{prasanna.310892@gmail.com} | 720.755.7888
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 	COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Colorado,
Boulder}
\descript{Master's in Computer Science}
\location{May 2018 | Boulder, CO \\ Cum. GPA: 3.94/4.0}
\sectionsep

\subsection{R.V. College of Engineering}
\descript{B E in Information Science}
\location{July 2014 | Bangalore, India}
\location{ Cum. GPA: 8.72 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Link}
LinkedIn://  \href{https://www.linkedin.com/in/prasanna25169}{\custombold{prasanna25169}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Java \textbullet{}Python \textbullet{} C \textbullet{} C++ \\
%\sectionsep
\subsection{Query Languages}
MySQL \textbullet{}PostgreSQL \textbullet{} NoSQL\\
%\sectionsep
\subsection{Data-Exchange Format}
JSON \textbullet{} XML \textbullet{} XSD \textbullet{} WSDL \\
%\sectionsep
\subsection{FrontEnd Skills}
HTML5 \textbullet{} CSS3 \textbullet{} JS ES6 \textbullet{} JQuery \textbullet{}
JSP \textbullet{} Node.js \textbullet{} React.js
\subsection{IDE }
IntelliJ \textbullet{} Eclipse \textbullet{} PyCharm \textbullet{} Jupyter Notebook\\
\subsection{Other }
Hibernate \textbullet{} MyBatis \textbullet{} DropwizardIO  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Big Data Architecture\\
Object Oriented Analysis and Design \\
Design and Analysis of Algorithms \\
Network systems \\
Convex Optimization \\
Linear Programming \\
Deep Neural Networks \\
Machine Learning \\

\sectionsep 
\subsection{Undergraduate}
Algorithms \\
Data Structures with C \\
Java and J2EE\\
Operating Systems \\
Web Programming \\
Advanced Unix\\
Database Management Systems\\
Data Mining\\
Optimization Techniques\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% 	COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Objective}
%\location{To secure an internsip for Summer 2017}
%%%%
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{HomeAway.com, Inc.}
\descript{| Software Developer}
\location{May 2018 - Present | Austin,TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Working in traveler and partner authentication, service to service authorization and user management system
\item Closely involved in apps cloud migration by rebuilding a scalable and resilient authentication systems encashing on the latest applicable frameworks
\item Developed runtime spam protection systems , integrated cloud based notification , migrated legacy apps to latest devops systems.
\item Technologies working on - C* ,Java ,React.js ,Redis ,Jwt ,Dropwizard ,Kafka
\end{tightemize}
\sectionsep

\runsubsection{HomeAway.com, Inc.}
\descript{| Software Developer Intern}
\location{June 2017 - August 2017 | Austin,TX}
\begin{tightemize}
\item Participated in the HomeAway University program for first 2 weeks.
\item Developed an payment information dashboard to swiftly analyze and resolve the payment records which failed.
\item Developed using dropwizard,react,mybatis,node and internal homeaway architecture patterns.
\end{tightemize}
\sectionsep

\runsubsection{Via.com}
\descript{| Software Developer}
\location{July 2014 - June 2016 | Bangalore,India}
\begin{tightemize}
\item Created full-fledged travel e-commerce site as training in 2 months.
\item Integrated multiple vendor APIs to delegate the inventory content for hotels.
\item Developed generic email framework scalable for multiple organisation email.
\item Introduced pay later feature for the hotels.
\item Built all the backend endpoints for the revamped UI experience of the site. 
\end{tightemize}
\sectionsep

\runsubsection{Deloitte Consulting LLP}
\descript{| BTA-Intern }
\location{February 2014 – June 2014 | Bangalore,India}
\begin{tightemize}
\item Worked on a the integration of social media platform to company specific ERP in order to reduce the response time required  for tending to customer queries using MuleSoft  an iPaaS tool.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 	Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Projects}
\runsubsection{Twitter stream opinion mining}
\location{January 2018 – May 2018 | Boulder}
\begin{tightemize}
\item  Visualization of the aspect-based opinions for a given product in real time as a heat map based on demographics using live twitter stream data.
\item Developed as part of Big Data Architecture coursework.
\item Developed using Spark,Kafka ,OpenNLP , Google maps ,Redis ,Java ,React.js
\end{tightemize}
\sectionsep

\runsubsection{Melody milieu}
\location{August 2017 – Dec 2017 | Boulder}
\begin{tightemize}
\item Built secure webapp RESTful endpoints based on object oriented principles, to produce song recommendation based on user history.
\item Developed as part of Object Oriented Analysis and Design Principles course.
\item Developed utilizing micro services pattern. Used SpringBoot, Java.
\end{tightemize}
\sectionsep
	
\runsubsection{US-36 Toll optimization}
\location{August 2016 – Dec 2016 | Boulder}
\begin{tightemize}
\item Built using  Python, HTML, JavaScript, jQuery, CSS3, Gurobi.
\item Developed an utility that would optimize the driving time with toll cost incurred by the users in US 36 highway, with options to fine tune cost and time.
\end{tightemize}
\sectionsep


\end{minipage}
\end{document}  \documentclass[]{article}






